---
title: "final_project"
author: "Naomi-Grace Jennings"
date: "10/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(tidyverse)
library(stringr)
library(ggplot2)
library(dplyr)
library(ggthemes)
library(sentimentr)
library(glue)
library(tidytext)
library(rstanarm)
library(broom.mixed)
library(gtsummary)
library(gt)
```

Artist  g1
```{r}

#Creating a list item of artists I want to use 
#Used web developer tools to find correct artist name

artists1 <- c("kurtis_blow", "grandmaster_melle_mel", "run_dmc", "ll_cool_j", "slick_rick", "ice_cube", "nwa", "redman")

#Url list paste0() to add the artist's name from artist1 list above

artist_urls <- paste0("https://www.allthelyrics.com/lyrics/", artists1)


finaldata1 <- c() #setting up an empty dataset for the end

#Webscraper: goes through each url pasted above 

for (j in 1:length(artist_urls)) {
  
  all <- read_html(artist_urls[j])
  
  
 # lyrics  for each url under each artist   
  raps <- all %>%
    html_nodes(".lyrics-list-item") %>%
    # html_attr("href")
    html_text()
  
  raps # Here are the lyrics for each song
  
  
  urls <- all %>%
    html_nodes("a") %>%
    html_attr("href")
  
  urls.d <- data.frame(webpage = urls, line = 1:length(urls))
  raps.d <- data.frame(titles = raps, artist = "Eminem")
  
  
  lyric_data1 <- urls.d %>%
    slice(-(1:38)) %>%
    head(-13) %>%
    mutate(Artist = artists1[j]) %>%
    mutate(titles = raps) %>%
    mutate(line = NULL) %>%
    mutate(webpage = paste0("https://www.allthelyrics.com", webpage))
  
  lyrics1 <- c()
  
  for(i in 1:length(lyric_data1$webpage)){ 
    
    words <- read_html(lyric_data1$webpage[i])
    lyrics1[i] <- words %>%
      html_nodes(".content-text-inner") %>%
      html_text()
    
  }
  
  lyric_data_words1 <- lyric_data1 %>%
    mutate(words = lyrics1)
  
  finaldata1 <- rbind(finaldata1, lyric_data_words1)
  
  
}

View(finaldata1)

write.csv(finaldata1, "finaldata.csv")
```


Artists g2
```{r}
artists2 <- c("nas", "notorious_big", "2pac", "dmx", "jayz", "eminem", "50_cent", "ti") 

artist_urls <- paste0("https://www.allthelyrics.com/lyrics/", artists2)

finaldata2 <- c() #setting up an empty dataset for the end


for (j in 1:length(artist_urls)) {
  
  all <- read_html(artist_urls[j])
  
  raps <- all %>%
    html_nodes(".lyrics-list-item") %>%
    # html_attr("href")
    html_text()
  
  raps # Here are the raps
  
  
  urls <- all %>%
    html_nodes("a") %>%
    html_attr("href")
  
  urls.d <- data.frame(webpage = urls, line = 1:length(urls))
  raps.d <- data.frame(titles = raps, artist = "Eminem")
  
  
  lyric_data2 <- urls.d %>%
    slice(-(1:38)) %>%
    head(-13) %>%
    mutate(Artist = artists2[j]) %>%
    mutate(titles = raps) %>%
    mutate(line = NULL) %>%
    mutate(webpage = paste0("https://www.allthelyrics.com", webpage))
  
  lyrics2 <- c()
  
  for(i in 1:length(lyric_data2$webpage)){ 
    
    words <- read_html(lyric_data2$webpage[i])
    lyrics2[i] <- words %>%
      html_nodes(".content-text-inner") %>%
      html_text()
    
  }
  
  lyric_data_words2 <- lyric_data2 %>%
    mutate(words = lyrics2)
  
  finaldata2 <- rbind(finaldata2, lyric_data_words2)
  
  
}

View(finaldata2)

write.csv(finaldata2, "finaldata.csv")
```


Artists g3
```{r}
artists3 <- c("too_short", "lil_wayne", "kanye_west","drake", "nicki_minaj")
#, "youngboy_never_broke_again", "snoop_dog", "j._cole")



artist_urls <- paste0("https://www.allthelyrics.com/lyrics/", artists3)

finaldata3 <- c() #setting up an empty dataset for the end


for (j in 1:length(artist_urls)) {
  
  all <- read_html(artist_urls[j])
  
  raps <- all %>%
    html_nodes(".lyrics-list-item") %>%
    # html_attr("href")
    html_text()
  
  raps # Here are the raps
  
  
  urls <- all %>%
    html_nodes("a") %>%
    html_attr("href")
  
  urls.d <- data.frame(webpage = urls, line = 1:length(urls))
  raps.d <- data.frame(titles = raps, artist = "Eminem")
  
  
  lyric_data3 <- urls.d %>%
    slice(-(1:38)) %>%
    head(-13) %>%
    mutate(Artist = artists3[j]) %>%
    mutate(titles = raps) %>%
    mutate(line = NULL) %>%
    mutate(webpage = paste0("https://www.allthelyrics.com", webpage))
  
  lyrics3 <- c()
  
  for(i in 1:length(lyric_data3$webpage)){ 
    
    words <- read_html(lyric_data3$webpage[i])
    lyrics3[i] <- words %>%
      html_nodes(".content-text-inner") %>%
      html_text()
    
  }
  
  lyric_data_words3 <- lyric_data3 %>%
    mutate(words = lyrics3)
  
  finaldata3 <- rbind(finaldata3, lyric_data_words3)
  
  
}

View(finaldata3)

write.csv(finaldata3, "finaldata.csv")





```

Artists g4
```{r}

artists4 <- c("grandmaster_caz", "kool_moe_dee", "spoonie_gee", "jimmy_spicer", "schoolly_d", "roxanne_shante", "beastie_boys", "krsone")

artist_urls <- paste0("https://www.allthelyrics.com/lyrics/", artists4)

finaldata4 <- c() #setting up an empty dataset for the end


for (j in 1:length(artist_urls)) {
  
  all <- read_html(artist_urls[j])
  
  raps <- all %>%
    html_nodes(".lyrics-list-item") %>%
    # html_attr("href")
    html_text()
  
  raps # Here are the raps
  
  
  urls <- all %>%
    html_nodes("a") %>%
    html_attr("href")
  
  urls.d <- data.frame(webpage = urls, line = 1:length(urls))
  raps.d <- data.frame(titles = raps, artist = "Eminem")
  
  
  lyric_data4 <- urls.d %>%
    slice(-(1:38)) %>%
    head(-13) %>%
    mutate(Artist = artists4[j]) %>%
    mutate(titles = raps) %>%
    mutate(line = NULL) %>%
    mutate(webpage = paste0("https://www.allthelyrics.com", webpage))
  
  lyrics4 <- c()
  
  for(i in 1:length(lyric_data4$webpage)){ 
    
    words <- read_html(lyric_data4$webpage[i])
    lyrics4[i] <- words %>%
      html_nodes(".content-text-inner") %>%
      html_text()
    
  }
  
  lyric_data_words4 <- lyric_data4 %>%
    mutate(words = lyrics4)
  
  finaldata4 <- rbind(finaldata4, lyric_data_words4)
  
  
}

View(finaldata4)

write.csv(finaldata4, "finaldata4.csv")
```


Artists g5
```{r}
artists5 <- c("schoolly_d", "chuck_d", "big_daddy_kane", "kool_g_rap", "grand_puba", "scarface", "dr_dre", "dres") 

artist_urls <- paste0("https://www.allthelyrics.com/lyrics/", artists5)

finaldata5 <- c() #setting up an empty dataset for the end


for (j in 1:length(artist_urls)) {
  
  all <- read_html(artist_urls[j])
  
  raps <- all %>%
    html_nodes(".lyrics-list-item") %>%
    # html_attr("href")
    html_text()
  
  raps # Here are the raps
  
  
  urls <- all %>%
    html_nodes("a") %>%
    html_attr("href")
  
  urls.d <- data.frame(webpage = urls, line = 1:length(urls))
  raps.d <- data.frame(titles = raps, artist = "Eminem")
  
  
  lyric_data5 <- urls.d %>%
    slice(-(1:38)) %>%
    head(-13) %>%
    mutate(Artist = artists5[j]) %>%
    mutate(titles = raps) %>%
    mutate(line = NULL) %>%
    mutate(webpage = paste0("https://www.allthelyrics.com", webpage))
  
  lyrics5 <- c()
  
  for(i in 1:length(lyric_data5$webpage)){ 
    
    words <- read_html(lyric_data5$webpage[i])
    lyrics5[i] <- words %>%
      html_nodes(".content-text-inner") %>%
      html_text()
    
  }
  
  lyric_data_words5 <- lyric_data5 %>%
    mutate(words = lyrics5)
  
  finaldata5 <- rbind(finaldata5, lyric_data_words5)
  
  
}

View(finaldata5)

write.csv(finaldata5, "finaldata5.csv")
```

Artists g6 
```{r}
artists6 <- c("method_man", "raekwon", "prodigy", "busta_rhymes", "twista", "big_pun", "lauryn_hill", "ghostface_killah") 

artist_urls <- paste0("https://www.allthelyrics.com/lyrics/", artists6)

finaldata6 <- c() #setting up an empty dataset for the end


for (j in 1:length(artist_urls)) {
  
  all <- read_html(artist_urls[j])
  
  raps <- all %>%
    html_nodes(".lyrics-list-item") %>%
    # html_attr("href")
    html_text()
  
  raps # Here are the raps
  
  
  urls <- all %>%
    html_nodes("a") %>%
    html_attr("href")
  
  urls.d <- data.frame(webpage = urls, line = 1:length(urls))
  raps.d <- data.frame(titles = raps, artist = "Eminem")
  
  
  lyric_data6 <- urls.d %>%
    slice(-(1:38)) %>%
    head(-13) %>%
    mutate(Artist = artists6[j]) %>%
    mutate(titles = raps) %>%
    mutate(line = NULL) %>%
    mutate(webpage = paste0("https://www.allthelyrics.com", webpage))
  
  lyrics6 <- c()
  
  for(i in 1:length(lyric_data6$webpage)){ 
    
    words <- read_html(lyric_data6$webpage[i])
    lyrics6[i] <- words %>%
      html_nodes(".content-text-inner") %>%
      html_text()
    
  }
  
  lyric_data_words6 <- lyric_data6 %>%
    mutate(words = lyrics6)
  
  finaldata6 <- rbind(finaldata6, lyric_data_words6)
  
  
}

View(finaldata6)

write.csv(finaldata6, "finaldata6.csv")
```


Artists g7 
```{r}
artists7 <- c("ludacris", "jadakiss", "common", "gucci_mane", "rick_ross")

artist_urls <- paste0("https://www.allthelyrics.com/lyrics/", artists7)

finaldata7 <- c() #setting up an empty dataset for the end


for (j in 1:length(artist_urls)) {
  
  all <- read_html(artist_urls[j])
  
  raps <- all %>%
    html_nodes(".lyrics-list-item") %>%
    # html_attr("href")
    html_text()
  
  raps # Here are the raps
  
  
  urls <- all %>%
    html_nodes("a") %>%
    html_attr("href")
  
  urls.d <- data.frame(webpage = urls, line = 1:length(urls))
  raps.d <- data.frame(titles = raps, artist = "Eminem")
  
  
  lyric_data7 <- urls.d %>%
    slice(-(1:38)) %>%
    head(-13) %>%
    mutate(Artist = artists7[j]) %>%
    mutate(titles = raps) %>%
    mutate(line = NULL) %>%
    mutate(webpage = paste0("https://www.allthelyrics.com", webpage))
  
  lyrics7 <- c()
  
  for(i in 1:length(lyric_data7$webpage)){ 
    
    words <- read_html(lyric_data7$webpage[i])
    lyrics7[i] <- words %>%
      html_nodes(".content-text-inner") %>%
      html_text()
    
  }
  
  lyric_data_words7 <- lyric_data7 %>%
    mutate(words = lyrics7)
  
  finaldata7 <- rbind(finaldata7, lyric_data_words7)
  
  
}

View(finaldata7)

write.csv(finaldata7, "finaldata7.csv")
```


Artists g8 

```{r}
artists8 <- c("killer_mike", "korn", "2_live_crew", "lil_boosie")
             
artist_urls <- paste0("https://www.allthelyrics.com/lyrics/", artists8)

finaldata8 <- c() #setting up an empty dataset for the end


for (j in 1:length(artist_urls)) {
  
  all <- read_html(artist_urls[j])
  
  raps <- all %>%
    html_nodes(".lyrics-list-item") %>%
    # html_attr("href")
    html_text()
  
  raps # Here are the raps
  
  
  urls <- all %>%
    html_nodes("a") %>%
    html_attr("href")
  
  urls.d <- data.frame(webpage = urls, line = 1:length(urls))
  raps.d <- data.frame(titles = raps, artist = "Eminem")
  
  
  lyric_data8 <- urls.d %>%
    slice(-(1:38)) %>%
    head(-13) %>%
    mutate(Artist = artists8[j]) %>%
    mutate(titles = raps) %>%
    mutate(line = NULL) %>%
    mutate(webpage = paste0("https://www.allthelyrics.com", webpage))
  
  lyrics8 <- c()
  
  for(i in 1:length(lyric_data8$webpage)){ 
    
    words <- read_html(lyric_data8$webpage[i])
    lyrics8[i] <- words %>%
      html_nodes(".content-text-inner") %>%
      html_text()
    
  }
  
  lyric_data_words8 <- lyric_data8 %>%
    mutate(words = lyrics8)
  
  finaldata8 <- rbind(finaldata8, lyric_data_words8)
  
  
}

View(finaldata8)

write.csv(finaldata8, "finaldata8.csv")
```



```{r}
#Merging all data into one dataset w/all artists, lyrics, titles

#Using rbind() to make a new .csv and changed colnames for ease of access

complete_data <- rbind(finaldata1, finaldata2, finaldata3, finaldata4, finaldata5, finaldata6, finaldata7, finaldata8)
write.csv(complete_data, "complete_data.csv")

 

  colnames(complete_data) <- c("webpage", "artist", "title", "words")
```





Average number of words used per artist/song
```{r}
avg_words <- complete_data %>%
  
  #select(artist, words, title) %>%
  group_by(artist, title) %>%
    
 mutate(bitch = sum(str_count(words, "bitch")),
           hoe = sum(str_count(words, "hoe")), 
           slut = sum(str_count(words, "slut")),
           whore = sum(str_count(words, "whore")), 
           tease = sum(str_count(words, "tease")), 
           trick = sum(str_count(words, "trick")),
           gold_digger = sum(str_count(words, "gold digger"))) %>%
  
  #maybe group by title here again then summarise so all the zero rows don't show up...?? Looks messy 
  
  mutate(sumrow = bitch + hoe + slut + whore + tease + trick + gold_digger)
        

        
#ggplot average number of terms used by all artists per song

   avg_words_model <- avg_words %>%
     group_by(artist) %>%
     summarise(avg_count = mean(sumrow)) %>%
     
   
   ggplot(aes(x = factor(artist, level = c("grandmaster_caz", "grandmaster_melle_mel", "kurtis_blow", "kool_moe_dee", "spoonie_gee", "jimmy_spicer",  "run_dmc", "ll_cool_j", "roxanne_shante", "slick_rick", "beastie_boys", "lil_boosie",  "krsone", "too_short", "schoolly_d", "ice_cube", "chuck_d", "grand_puba", "kool_g_rap", "big_daddy_kane", "nwa", "method_man",  "scarface", "dres", "redman", "nas", "notorious_big", "2pac", "raekwon", "prodigy", "busta_rhymes", "twista", "dmx", "jayz", "2_live_crew", "big_pun", "lauryn_hill", "eminem", "ghostface_killah", "ludacris", "jadakiss", "korn", "dr_dre", "50_cent", "common", "killer_mike", "ti",  "lil_wayne", "gucci_mane", "rick_ross",  "kanye_west","drake", "nicki_minaj")), y = avg_count)) +
  geom_col(aes(stat = "identity", position = "stack"), color = "skyblue", fill = "darkblue") +
   labs(title = "Misogynistic Terms in Popular Rap", subtitle = "Average number of misogynistic terms used per song by the popular rappers from 1979-2016 ", x = "Artist", y = "Misogynistic Terms") +
   theme(axis.text.x = element_text(angle = 90)) +
     scale_x_discrete(labels = c("Grandmaster Caz", "Grandmaster Melle Mel", "Kurtis Blow", "Kool Moe Dee", "Spoonie Gee", "Jimmy Spicer",  "Run-DMC", "LL Cool J", "Roxanne Shante", "Slick Rick", "Beastie Boys", "Lil Boosie",  "KRS-One", "Too $hort", "Schoolly D", "Ice Cube", "Chuck D", "Grand Puba", "Kool G Rap", "Big Daddy Kane", "NWA", "Method Man",  "Scarface", "Dres", "Redman", "Nas", "Notorious B.I.G.", "2Pac", "Raekwon", "Prodigy", "Busta Rhymes", "Twista", "DMX", "Jay-Z", "2 Live Crew", "Big Pun", "Lauryn Hill", "Eminem", "Ghostface Killah", "Ludacris", "Jadakiss", "Korn", "D. Dre", "50 Cent", "Common", "Killer Mike", "T.I.",  "Lil Wayne", "Gucci Mane", "Rick Ross",  "Kanye West","Drake", "Nicki Minaj")) +
     theme_clean() +
     theme(axis.text.x = element_text(angle = 90)) 
   
avg_words_model
```

Total word count per artist model 
```{r}
total_count <- complete_data %>%
  
  select(artist, words, title) %>%
  group_by(title) %>%

           
           
  mutate(bitch = sum(str_count(words, "bitch")),
            hoe = sum(str_count(words, "hoe")), 
            slut = sum(str_count(words, "slut")),
           whore = sum(str_count(words, "whore")), 
            tease = sum(str_count(words, "tease")), 
            trick = sum(str_count(words, "trick")),
            gold_digger = sum(str_count(words, "gold digger"))) %>% 

   group_by(artist) %>%
   mutate(sumrow = sum(c(bitch, hoe, slut, whore, tease, trick, gold_digger))) 
  

total_count_model <- total_count%>%

ggplot(aes(x = factor(artist, level = c("grandmaster_caz", "grandmaster_melle_mel", "kurtis_blow", "kool_moe_dee", "spoonie_gee", "jimmy_spicer",  "run_dmc", "ll_cool_j", "roxanne_shante", "slick_rick", "beastie_boys", "lil_boosie",  "krsone", "too_short", "schoolly_d", "ice_cube", "chuck_d", "grand_puba", "kool_g_rap", "big_daddy_kane", "nwa", "method_man",  "scarface", "dres", "redman", "nas", "notorious_big", "2pac", "raekwon", "prodigy", "busta_rhymes", "twista", "dmx", "jayz", "2_live_crew", "big_pun", "lauryn_hill", "eminem", "ghostface_killah", "ludacris", "jadakiss", "korn", "dr_dre", "50_cent", "common", "killer_mike", "ti",  "lil_wayne", "gucci_mane", "rick_ross",  "kanye_west","drake", "nicki_minaj")), y = sumrow)) +
  geom_col( color = "darkblue", fill = "darkblue", color = "skyblue") +
   labs(title = "Misogynistic Words used by Popular Rappers", subtitle = "From 1979-2016",  x = "Artist", y = "Total Word Count") +
   
     scale_x_discrete(labels = c("Grandmaster Caz", "Grandmaster Melle Mel", "Kurtis Blow", "Kool Moe Dee", "Spoonie Gee", "Jimmy Spicer",  "Run-DMC", "LL Cool J", "Roxanne Shante", "Slick Rick", "Beastie Boys", "Lil Boosie",  "KRS-One", "Too $hort", "Schoolly D", "Ice Cube", "Chuck D", "Grand Puba", "Kool G Rap", "Big Daddy Kane", "NWA", "Method Man",  "Scarface", "Dres", "Redman", "Nas", "Notorious B.I.G.", "2Pac", "Raekwon", "Prodigy", "Busta Rhymes", "Twista", "DMX", "Jay-Z", "2 Live Crew", "Big Pun", "Lauryn Hill", "Eminem", "Ghostface Killah", "Ludacris", "Jadakiss", "Korn", "D. Dre", "50 Cent", "Common", "Killer Mike", "T.I.",  "Lil Wayne", "Gucci Mane", "Rick Ross",  "Kanye West","Drake", "Nicki Minaj")) +
  theme_clean() +
theme(axis.text.x = element_text(angle = 90)) 
        
total_count_model
        
```








"grandmaster_caz", "grandmaster_melle_mel", "kurtis_blow", "kool_moe_dee", "spoonie_gee", "jimmy_spicer",  "run_dmc", "ll_cool_j", "roxanne_shante", "slick_rick", "beastie_boys", "lil_boosie",  "krsone", "too_short", "schoolly_d", "ice_cube", "chuck_d", "grand_puba", "kool_g_rap", "big_daddy_kane", "nwa", "method_man",  "scarface", "dres", "redman", "nas", "notorious_big", "2pac", "raekwon", "prodigy", "busta_rhymes", "twista", "dmx", "jayz", "2_live_crew", "big_pun", "lauryn_hill", "eminem", "ghostface_killah", "ludacris", "jadakiss", "korn", "dr_dre", "50_cent", "common", "killer_mike", "ti",  "lil_wayne", "gucci_mane", "rick_ross",  "kanye_west","drake", "nicki_minaj"    
      

Song Sentiment distribution for an individual artist (Too $hort)
```{r}
#Sentiments for too short (total)
# too_short <- complete_data %>%
#   filter(Artist == "too_short") %>%
#   select(words, Artist, titles)
# 
#  too_short_sentiments <- sentiment_by(too_short$words,
#  averaging.function = sentimentr::average_downweighted_zero) %>%
#     mutate(total = sum(ave_sentiment)) 
 
 too_short_sentiments <- complete_data %>%
   filter(artist == "too_short") %>%
  select(words, artist, title) %>%
   group_by(title) %>%
   get_sentences() %>%
   
 
sentiment_by(too_short_sentiments$words, by = "title",  
 averaging.function = sentimentr::average_mean) %>%
   group_by(title)

#modeling one artists sentiments each song 
too_short_sentiments %>%
  select(title, ave_sentiment) %>%
  group_by(title) %>%
  summarise(mean = mean(ave_sentiment)) %>%


  
 
 ggplot(aes(x = reorder(title, desc(mean)), y = mean)) +
   geom_col(color = "darkblue", fill = "steelblue") +
  
  labs(title = "Too $hort Sentiment Ratings", subtitle = "Sentiment Ratings of Too $hort songs", y = "Average Sentiment Rating for each Too $hort Song", x = "Songs") +
  theme_clean() +
theme(axis.text.x = element_blank()) 

too_short_sentiments
  
  
```




whole dataset sentiments (averge sentiment rating for each artist)
```{r}
total_sentiments <- complete_data %>%
   
  select(words, artist, title) %>%
   group_by(artist, title) %>%
   get_sentences() %>%
   
 
sentiment_by(total_sentiments$words, by = c("artist", "title"),  
 averaging.function = sentimentr::average_mean) 

total_sentiments <- total_sentiments%>%
  rename(song_sentiment = ave_sentiment)



total_avg_sentiments <- total_sentiments %>%
  group_by(artist) %>%
  summarise(avg_song_sentiment = sum(song_sentiment)) 
  
total_avg_sentiments_model <- total_avg_sentiments %>%
 ggplot(aes(x = factor(artist, level = c("grandmaster_caz", "grandmaster_melle_mel", "kurtis_blow", "kool_moe_dee", "spoonie_gee", "jimmy_spicer",  "run_dmc", "ll_cool_j", "roxanne_shante", "slick_rick", "beastie_boys",  "krsone", "too_short", "schoolly_d", "ice_cube", "chuck_d", "grand_puba", "kool_g_rap", "big_daddy_kane", "nwa", "method_man",  "scarface", "dres", "redman", "nas", "notorious_big", "2pac", "raekwon", "prodigy", "busta_rhymes", "twista", "dmx", "jayz", "big_pun", "lauryn_hill", "eminem", "ghostface_killah", "ludacris", "jadakiss", "dr_dre", "50_cent", "common", "ti",  "lil_wayne", "gucci_mane", "rick_ross",  "kanye_west","drake", "nicki_minaj")), y = avg_song_sentiment)) +
   geom_col(fill = "steelblue", color = "darkblue") +
  
  scale_x_discrete(labels = c("Grandmaster Caz", "Grandmaster Melle Mel", "Kurtis Blow", "Kool Moe Dee", "Spoonie Gee", "Jimmy Spicer",  "Run-DMC", "LL Cool J", "Roxanne Shante", "Slick Rick", "Beastie Boys", "Lil Boosie",  "KRS-One", "Too $hort", "Schoolly D", "Ice Cube", "Chuck D", "Grand Puba", "Kool G Rap", "Big Daddy Kane", "NWA", "Method Man",  "Scarface", "Dres", "Redman", "Nas", "Notorious B.I.G.", "2Pac", "Raekwon", "Prodigy", "Busta Rhymes", "Twista", "DMX", "Jay-Z", "2 Live Crew", "Big Pun", "Lauryn Hill", "Eminem", "Ghostface Killah", "Ludacris", "Jadakiss", "Korn", "D. Dre", "50 Cent", "Common", "Killer Mike", "T.I.",  "Lil Wayne", "Gucci Mane", "Rick Ross",  "Kanye West","Drake", "Nicki Minaj")) +
  labs(title = "Average Sentiment Ratings for Popular Rappers", subtitle = "From 1979-2016", x = "Artist", y = "Average Sentiment Rating") +
  theme_clean() +
  theme(axis.text.x = element_text(angle = 90)) 
  
   
#average sentiment for all songs per artist over the years  
total_avg_sentiments_model
  
```
Sentiment alone is a very poor predictor of misogynistic sentiment or even sentiment in general...
  

Trying to find a way to show sentiment as it interacts with word usage 
```{r}
new_scores <- merge(total_sentiments, total_count) %>%
  mutate(sentiment_rating = case_when((song_sentiment >= 0 & sumrow <= 0) ~ "positive", 
                        # (ave_sentiment == 0) ~ "neutral", 
                         (song_sentiment <= 0 & sumrow >= 0) ~ "negative", 
                        TRUE ~ "neutral")) %>%
  
  mutate(sentiment_score = case_when(sentiment_rating == "positive" ~ -1, 
                   sentiment_rating == "neutral" ~ 0, 
                   sentiment_rating == "negative" ~ 1)) %>%
  group_by(artist) %>% 
    mutate(score = sum(sentiment_score))
  
 new_scores_model <- new_scores %>%
ggplot(aes(x = factor(artist, level = c("grandmaster_caz", "grandmaster_melle_mel", "kurtis_blow", "kool_moe_dee", "spoonie_gee", "jimmy_spicer",  "run_dmc", "ll_cool_j", "roxanne_shante", "slick_rick", "beastie_boys",  "krsone", "too_short", "schoolly_d", "ice_cube", "chuck_d", "grand_puba", "kool_g_rap", "big_daddy_kane", "nwa", "method_man",  "scarface", "dres", "redman", "nas", "notorious_big", "2pac", "raekwon", "prodigy", "busta_rhymes", "twista", "dmx", "jayz", "big_pun", "lauryn_hill", "eminem", "ghostface_killah", "ludacris", "jadakiss", "dr_dre", "50_cent", "common", "ti",  "lil_wayne", "gucci_mane", "rick_ross",  "kanye_west","drake", "nicki_minaj")), y = score)) +
 # geom_line(aes(group = 1)) +
  #geom_point() +
  geom_col(color = "steelblue", fill = "darkblue") +
  
  scale_x_discrete(labels = c("Grandmaster Caz", "Grandmaster Melle Mel", "Kurtis Blow", "Kool Moe Dee", "Spoonie Gee", "Jimmy Spicer",  "Run-DMC", "LL Cool J", "Roxanne Shante", "Slick Rick", "Beastie Boys", "Lil Boosie",  "KRS-One", "Too $hort", "Schoolly D", "Ice Cube", "Chuck D", "Grand Puba", "Kool G Rap", "Big Daddy Kane", "NWA", "Method Man",  "Scarface", "Dres", "Redman", "Nas", "Notorious B.I.G.", "2Pac", "Raekwon", "Prodigy", "Busta Rhymes", "Twista", "DMX", "Jay-Z", "2 Live Crew", "Big Pun", "Lauryn Hill", "Eminem", "Ghostface Killah", "Ludacris", "Jadakiss", "Korn", "D. Dre", "50 Cent", "Common", "Killer Mike", "T.I.",  "Lil Wayne", "Gucci Mane", "Rick Ross",  "Kanye West","Drake", "Nicki Minaj")) +
  theme(axis.text.x = element_text(angle = 90)) %>%
  labs(title = "Misogynistic Sentiment Ratings", subtitle = "For Artists between 1979-2016", x = "Artist", y = "Sentiment Rating") +
 
  theme_clean() +
  theme(axis.text.x = element_text(angle = 90)) 
new_scores_model
```




Word count and sentiment 
```{r}

 new_scores %>%

ggplot(aes(x = factor(artist, level = c("grandmaster_caz", "grandmaster_melle_mel", "kurtis_blow", "kool_moe_dee", "spoonie_gee", "jimmy_spicer",  "run_dmc", "ll_cool_j", "roxanne_shante", "slick_rick", "beastie_boys",  "krsone", "too_short", "schoolly_d", "ice_cube", "chuck_d", "grand_puba", "kool_g_rap", "big_daddy_kane", "nwa", "method_man",  "scarface", "dres", "redman", "nas", "notorious_big", "2pac", "raekwon", "prodigy", "busta_rhymes", "twista", "dmx", "jayz", "big_pun", "lauryn_hill", "eminem", "ghostface_killah", "ludacris", "jadakiss", "dr_dre", "50_cent", "common", "ti",  "lil_wayne", "gucci_mane", "rick_ross",  "kanye_west","drake", "nicki_minaj")), y = score)) +
 # geom_line(aes(group = 1)) +
  geom_point() +
  geom_line(aes(group = 1), color = "steelblue") +
  
  scale_x_discrete(labels = c("Grandmaster Caz", "Grandmaster Melle Mel", "Kurtis Blow", "Kool Moe Dee", "Spoonie Gee", "Jimmy Spicer",  "Run-DMC", "LL Cool J", "Roxanne Shante", "Slick Rick", "Beastie Boys", "Lil Boosie",  "KRS-One", "Too $hort", "Schoolly D", "Ice Cube", "Chuck D", "Grand Puba", "Kool G Rap", "Big Daddy Kane", "NWA", "Method Man",  "Scarface", "Dres", "Redman", "Nas", "Notorious B.I.G.", "2Pac", "Raekwon", "Prodigy", "Busta Rhymes", "Twista", "DMX", "Jay-Z", "2 Live Crew", "Big Pun", "Lauryn Hill", "Eminem", "Ghostface Killah", "Ludacris", "Jadakiss", "Korn", "D. Dre", "50 Cent", "Common", "Killer Mike", "T.I.",  "Lil Wayne", "Gucci Mane", "Rick Ross",  "Kanye West","Drake", "Nicki Minaj")) +
  theme(axis.text.x = element_text(angle = 90)) %>%
  labs(title = "Negative Sentiment Ratings", subtitle = "For Artists between 1979-2016", x = "Artist", y = "Negative Sentiment Rating") +
 
  theme_clean() +
  theme(axis.text.x = element_text(angle = 90)) 
new_scores_model2

```









`
 

 "grandmaster_caz", "kool_moe_dee", "spoonie_gee", "jimmy_spicer", "roxanne_shante", "beastie_boys", "krsone",   4
 
"schoolly_d", "chuck_d", "big_daddy_kane", "kool_g_rap", "grand_puba", "scarface", "dr_dre", "dres",    5

"method_man", "raekwon", "prodigy", "busta_rhymes", "twista", "big_pun", "lauryn_hill", "ghostface_killah",    6

"ludacris", "jadakiss", "common", "gucci_mane", "rick_ross",   7

"killer_mike", "korn", "2_live_crew", "lil_boosie"    8



Regression using all artists... 
```{r}
#adding spreadsheet with year and networth from excel to data I have rn 

# excel <- (read_csv("misogyny_in_rap/excel_data/excel2.csv")) %>%
#   select(!X4) %>%
#   rename(net = "Net Worth") %>%
#   rename(artist = "Artist")


  
#Dataset containing mutated misogyny ratings, artists, titles, year and net worth

# big <- merge(excel, new_scores)


#Stan_glm() to find something that is not there

fit_big <- stan_glm(data = big, 

#Looking at the year's effect on misogyny score

                    score ~  Year, 
                    family = gaussian(), 
                    refresh = 0)
print(fit_big, digits = 5)
```

Regression Model 
```{r}
regression <- tbl_regression(fit_big, intercept = TRUE) %>%
   as_gt()%>%
  tab_header(title = "Regression of Misogynistic Sentiment Ratings", 
             subtitle = "The Effect of Year on Misogynistic Sentiment in Rap Music") %>%
  theme_gtsummary_continuous2()

saveRDS(regression, file = "misogyny_in_rap")
saveRDS(new_scores_model, file = "misogyny_in_rap")
```

Linear regression??
```{r}
regression_model <- ggplot(big, aes(x = Year, y = sentiment_score)) +
  geom_point(color = "steelblue", alpha = .1, size = 1.5, position = position_jitter(width = 1.5, height = 1.5)) +
  labs(title = "Misogynistic Sentiment Rating and Year", x = "Year", y = "Rating") #+
  #geom_abline(intercept = -1017.40384, slope =   0.56448  , color = "darkblue")
  #This is just not cute but uses the coefficients from stan_glm() fit 
  

regression_model
  
 
```




```{r}
write.csv(big, "big.csv")

```

```{r}
 total_sentiments %>%
  filter(artist == "too_short") %>%
  group_by(title) %>%

#Here is the code I'll use for each artists' sentiment ratings (interactive portion)
   ggplot(aes(x = reorder(title, desc(song_sentiment)), y = song_sentiment)) +
   geom_col(color = "darkblue", fill = "steelblue") +
  
  labs(title = "Sentiment Ratings by Song", y = "Sentiment Rating", x = "Songs") +
  theme_clean() +
  theme(axis.text.x = element_blank()) 


  
  
```



